12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-04-21 rules/rules17.tex
Minor.

  The constant penalty for errors reflects the fact that any error (in
  a particular division) renders a solver untrustworthy for that
  division.  The value~$-4$ balances the community's interest in
  correct (thoroughly tested) solvers against the risk of stifling
  innovation: entering a perfect (but possibly buggy) solver into a
  division has a positive expected value if the probability of a
  soundness bug is below $\frac{1}{1+4} = 20$\,\%.

>>>>

  The constant penalty for errors reflects the fact that any error (in
  a particular division) renders a solver untrustworthy for that
  division.  The value~$4$ balances the community's strong interest in
  correct (thoroughly tested) solvers against the risk of stifling
  innovation: entering a (possibly buggy) solver that can solve all
  benchmarks into a division has a positive expected value if the
  probability of a soundness bug is below $\frac{1}{1+4} = 20$\,\%.
